Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
removed mildly significant

Our findings show that in both photos and Rewinds, believability was higher when participants were traveling alone. For photos, the difference in believability between those traveling alone and those traveling with company was 37\%, $\chi^2(1, N=82) = 5.137$, $p < .05$. For Rewinds, the difference was 12\%, $\chi^2(1, 127) = 1.865$, $p = 0.086 (<.1)$. The smaller difference suggests that Rewinds are more believable than photos for trips taken with company.

\subsubsection{Frequent Travelers}
% no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
% significant effects on video belivability $\chi^2(1,128) = 5.837$, p = 0.0079 (< 0.01)
% frequent - 86%, non-frequent - 65%
Participants who identified as frequent travelers found 86\% of Rewinds believable and accurate to their memory, while non-frequent travelers found 65\% of Rewinds believable, $\chi^2(1, 128) = 5.835$
$p < .05$. This suggests that Rewinds would be more suitable for a particular type of person.

\subsubsection{GPS Usage}
% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
% GPS - 69%, non-GPS - 81%
Our results show that participants who were non-regular GPS users found Rewinds believable more often than regular GPS users, suggesting the appropriate audience for Rewinds. Regular GPS users found Rewinds believable 69\% of the time, while non-regular users found Rewinds believable 84\% of the time, $\chi^2(1, 128) = 2.917$, $p < .05$.

@@

%\subsubsection{Travel Companions}
% no significant effects on photo desirability $\chi^2(1,94) = 0.071$, p = 0.3948(> 0.05)
% significant effects on video/trip desirability if alpha = 0.1 - $\chi^2(1, 133) = 2.443$, p = 0.059(< 0.1)
% alone - 13%, not alone - 26%
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$. The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.

>>>>

Our findings show that in both photos and Rewinds, believability was higher when participants were traveling alone. For photos, the difference in believability between those traveling alone and those traveling with company was 37\%, $\chi^2(1, N=82) = 5.137$, $p <.05$. For Rewinds, the difference was 12\%, $\chi^2(1, 127) = 1.865$, $p <.1)$. The smaller difference suggests that Rewinds are more believable than photos for trips taken with company.

\subsubsection{Frequent Travelers}
% no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
% significant effects on video belivability $\chi^2(1,128) = 5.837$, p = 0.0079 (< 0.01)
% frequent - 86%, non-frequent - 65%
Participants who identified as frequent travelers found 86\% of Rewinds believable and accurate to their memory, while non-frequent travelers found 65\% of Rewinds believable, $\chi^2(1, N=128) = 5.835$
$p < .05$. This suggests that Rewinds would be more suitable for a particular type of person.

\subsubsection{GPS Usage}
% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
% GPS - 69%, non-GPS - 81%
Our results show that participants who were non-regular GPS users found Rewinds believable more often than regular GPS users, suggesting the appropriate audience for Rewinds. Regular GPS users found Rewinds believable 69\% of the time, while non-regular users found Rewinds believable 84\% of the time, $\chi^2(1, N=128) = 2.917$, $p < .05$.

@@

%\subsubsection{Travel Companions}
% no significant effects on photo desirability $\chi^2(1,94) = 0.071$, p = 0.3948(> 0.05)
% significant effects on video/trip desirability if alpha = 0.1 - $\chi^2(1, 133) = 2.443$, p = 0.059(< 0.1)
% alone - 13%, not alone - 26%
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. This difference is however not significant $\chi^2(1, N=127) = 1.865$, $p <.1)$, although the data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
